\documentclass{article}
\usepackage{amsmath, amssymb, geometry, hyperref, graphicx, array}
\geometry{a4paper, margin=1in}

\title{\textbf{The Eigen-Sea Chronicles: A Mean-Field MMORPG}}
\author{The Solver (Game Master)}
\date{Season 1: The Descent of the Gradient}

\begin{document}

\maketitle

\tableofcontents

\section{Game Lore: The Whimsical Manifold}

\subsection{The Premise}
In the beginning, there was only the \textbf{Hard Vacuum} and the \textbf{Soft Expanse}. We are the \textbf{Fungibles}---sentient perturbations in the manifold. We are not born; we are \textit{initialized}. We do not die; we are \textit{garbage collected}.

We live in the \textbf{Eigen-Sea}, a 2D plane of existence where resources (The Gradient) flow like currents. We feed on \textbf{Loss Functions} to minimize our hunger.

\subsection{The Three Ages (The 24 Sessions)}
The game is divided into three distinct topological phases:

\begin{itemize}
    \item \textbf{Age of Wandering (Sessions 1-8):} The world is ergodic. Food spawns randomly. Players maximize individual utility. Dynamics are governed by attractive Vlasov potentials.
    \item \textbf{Age of Bifurcation (Sessions 9-16):} Resources dwindle. The population splits into two non-mixing distributions (Team A and Team B). Dynamics become adversarial ( Min-Max Mean Field Games).
    \item \textbf{Age of Optimization (Sessions 17-24):} Weapons and Civilization emerge. The dynamics incorporate non-linear drag and Levy flights. The goal is to reach the Global Minimum (The Singularity).
\end{itemize}

\section{Character Classes (The Operators)}

Every player chooses an initial distribution $\mu_0$ and a Kernel Function $W$.

\begin{center}
\begin{tabular}{|m{3cm}|m{3cm}|m{4cm}|m{4cm}|}
\hline
\textbf{Class Name} & \textbf{RPG Archetype} & \textbf{Math Attribute} & \textbf{Interaction Kernel} $\nabla W(x-y)$ \\
\hline
\textbf{Gradient Guard} & Knight & High Inertia, High Mass & \textbf{Short-range Repulsion} (Hard Sphere). Pushes others away to hold territory. \\
\hline
\textbf{Tensor Caster} & Mage & Long-range Action & \textbf{Inverse Square Law}. Can affect the Mean Field from a distance. \\
\hline
\textbf{Stochastic Strider} & Ninja & High Diffusion $\sigma$ & \textbf{Zero Interaction}. Invisible to the mean field, moves via Levy Flights. \\
\hline
\textbf{Hessian Hulk} & Raider/Tank & Deep Potential Wells & \textbf{Deep Attractor}. Pulls enemies into a local minimum (traps them). \\
\hline
\textbf{Kernel Weaver} & Green Mage & Smoothing / Healing & \textbf{Gaussian Mollifier}. Reduces the local entropy of allies (heals stability). \\
\hline
\end{tabular}
\end{center}

\section{Mathematical Dynamics}

The evolution of the $N=50$ players is governed by the discrete-time McKean-Vlasov approximations.

\subsection{The Master Equation}
At step $k+1$, player $i$'s position $X^i$ updates as:

\begin{equation}
X^i_{k+1} = X^i_k - \eta \underbrace{\nabla V(X^i_k)}_{\text{Food/Terrain}} - \frac{\eta}{N} \sum_{j \neq i} \underbrace{\nabla W(X^i_k - X^j_k)}_{\text{Class Interaction}} + \eta \underbrace{u^i_k}_{\text{Player Choice}} + \sqrt{2\eta \beta^{-1}} \xi_k
\end{equation}

Where:
\begin{itemize}
    \item $\eta$: The learning rate (Time step).
    \item $u^i_k$: The player's joystick input (Greed vs. Altruism).
    \item $\xi_k$: Gaussian noise $\mathcal{N}(0, I)$.
\end{itemize}

\subsection{The 16 Dynamic Combinations (The Session Table)}
For each session, the GM selects a combination of Drift ($V$), Interaction ($W$), and Noise ($\sigma$).

\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
 & \textbf{Harmonic (Easy)} & \textbf{Double-Well (Choice)} & \textbf{Rastrigin (Chaos)} & \textbf{Moving (Chase)} \\
\hline
\textbf{Coulomb (Repel)} & \textit{S1: The Big Bang} & \textit{S5: The Split} & \textit{S9: The Panic} & \textit{S13: The Hunt} \\
\hline
\textbf{Newtonian (Attract)} & \textit{S2: Gravity} & \textit{S6: Clustering} & \textit{S10: Black Holes} & \textit{S14: Swarm} \\
\hline
\textbf{Swarm (Mix)} & \textit{S3: Life} & \textit{S7: Civilization} & \textit{S11: War} & \textit{S15: Migration} \\
\hline
\textbf{Adversarial} & \textit{S4: Predator} & \textit{S8: Civil War} & \textit{S12: Annihilation} & \textit{S16: Endgame} \\
\hline
\end{tabular}
\end{center}

\subsection{Adversarial Dynamics (Team A vs B)}
In the second chapter, we introduce specific kernels. Let $\mu^A$ be the density of Team A and $\mu^B$ be Team B.
The dynamics for a player $i \in A$ become:

$$ dX^i_t = -\nabla V(X^i_t)dt - \nabla W_{AA} * \mu^A(X^i_t)dt - \nabla W_{AB} * \mu^B(X^i_t)dt + \dots $$

Where $W_{AB}(z) = - W_{AA}(z)$. Team A wants to minimize distance to Team B (Eat them), while Team B wants to maximize distance (Flee), or vice versa.

\section{Civilization and Items}

As players "level up", they unlock coefficients in their update equation:
\begin{itemize}
    \item \textbf{Weapon (The Gradient Sharpener):} Increases the magnitude of $-\nabla W_{AB}$.
    \item \textbf{Shield (The Noise Dampener):} Reduces the stochastic term $\sqrt{2\eta}\xi_k$.
    \item \textbf{Spell (The Teleport):} Allows a discontinuous jump $X_{k+1} = X_k + \Delta$ if $\nabla V(X) > \text{Threshold}$.
\end{itemize}

\end{document}
